Meta-analysis

### 2020-05-27 04_MetaAnalysis.Rmd
Correct treatment means plot Move library(metafor) to pacman at the top of the document

```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer, netmeta)

@@

```{r treatment_means_plot}
slimmer_PM_dat$spray_management <-
   factor(slimmer_PM_dat$spray_management,
          levels(slimmer_PM_dat$spray_management)[rev(c(1, 2, 4, 5, 3))])

@@

```{r table_of_nTreatments}
kableExtra::kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year),
                  align = rep('c', 8)) %>%  #commented as was redering empty, needs a look in
   kable_styling(
      "striped",
      fixed_thead = TRUE,
      full_width = FALSE,
      position = "center"
   )
```
Treatments Late_plus and early don't have very good comparison to other treatments.

@@

slimmer_PM_dat %>%
   ggplot(aes(y = prop_yield_gain, x = spray_management)) +
   geom_boxplot() +
   #geom_point(position = "jitter", alpha = 1/5)+
   geom_jitter(width = 0.1, alpha = 1 / 5) +
   labs(x = "Spray management variable",
        y = "Grain yield (t/Ha)",
        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
   theme(plot.title = element_text(hjust = 0.5)) +
   geom_hline(yintercept = 0, linetype = 2) +
   coord_flip()
```

@@

```{r metafor_organisation}
library(metafor)
slimmer_PM_dat$spray_management <-
   factor(
      slimmer_PM_dat$spray_management,
      c(
         "control",
         "Early",
         "Recommended",
         "Recommended_plus",
         "Late_plus"
      )
   )

>>>>

```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer,metafor, netmeta)

@@

```{r treatment_means_plot}
# class spray_managment as a factor and reorder them for the plot
slimmer_PM_dat$spray_management <-
   factor(slimmer_PM_dat$spray_management,
          levels(factor(slimmer_PM_dat$spray_management))[rev(c(1, 2, 4, 5, 3))])

@@

```{r table_of_nTreatments}
kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year),
                  align = rep('c', 8),
      caption = "Which treatments and how many treatments are represented in each year") %>%  
   kable_styling(
      "striped",
      fixed_thead = TRUE,
      full_width = FALSE,
      position = "center"
   )
```
Treatments Late_plus and early don't have very good comparison to other treatments.

@@

slimmer_PM_dat %>%
   ggplot(aes(y = prop_yield_gain, x = spray_management)) +
   geom_boxplot() +
   #geom_point(position = "jitter", alpha = 1/5)+
   geom_jitter(width = 0.1, alpha = 1 / 5) +
   labs(x = "Spray management variable",
        y = "Grain yield (t/Ha)",
        title = "Mean grain yield difference to the control for each treatment \n categorised by spray management scenario") +
   theme(plot.title = element_text(hjust = 0.5)) +
   geom_hline(yintercept = 0, linetype = 2) +
   coord_flip()
```

@@

```{r metafor_organisation}
slimmer_PM_dat$spray_management <-
   factor(
      slimmer_PM_dat$spray_management,
      c(
         "control",
         "Early",
         "Recommended",
         "Recommended_plus",
         "Late_plus"
      )
   )
